Evolution of pre-copulatory and post-copulatory inbreeding behaviour

### 2016-10-13 ms_pre_post.Rmd
Revise first paragraph

Inbreeding often reduces the fitness of inbred offspring (termed 'inbreeding depression'), potentially driving evolution of inbreeding avoidance when inbreeding depression is strong [@Parker1979; @Parker2006; @Pusey1996; @Charlesworth1999; @Keller2002; @Charlesworth2009; @Szulkin2012]. For focal females, inbreeding avoidance might be acheived by avoiding related potential mates (pre-copulatory inbreeding avoidance), or by biasing fertilisation after mating has occurred so that related mates are less likely to sire offspring (post-copulatory inbreeding avoidance). Importantly, evolution of post-copulatory inbreeding avoidance requires that females be polyandrous, mating with multiple males during a single reproductive bout to ensure that post-copulatory choice is possible. As a reproductive strategy, polyandry thereby simultaneously allows females to choose multiple mates and creates the opportunity for further cryptic choice enacted through post-copulatory mechanisms. Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to reduce their inbreeding and therefore produce higher fitness offspring [@Zeh1997; @Jennions2000; @Tregenza2002; @Akcay2007]. However, it remains unclear  <!--- Just fix this last sentence somehow... --->

>>>>

Inbreeding often reduces the fitness of inbred offspring (termed 'inbreeding depression'), potentially driving evolution of inbreeding avoidance when inbreeding depression is strong [@Parker1979; @Parker2006; @Pusey1996; @Charlesworth1999; @Keller2002; @Charlesworth2009; @Szulkin2012]. For focal females, inbreeding avoidance might be acheived by avoiding related potential mates (pre-copulatory inbreeding avoidance), or by biasing fertilisation after mating has occurred so that related mates are less likely to sire offspring (post-copulatory inbreeding avoidance). Importantly, evolution of post-copulatory inbreeding avoidance requires that females be polyandrous, mating with multiple males during a single reproductive bout to ensure that post-copulatory choice can be expressed. As a reproductive strategy, polyandry thereby simultaneously allows females to choose multiple mates and creates the opportunity for further cryptic choice enacted through post-copulatory mechanisms. Polyandry has consequently been widely hypothesised to evolve as an adaptation to allow females to reduce their inbreeding and therefore produce higher fitness offspring [@Zeh1997; @Jennions2000; @Tregenza2002; @Akcay2007]. However, how pre- and post-copulatory strategies of inbreeding avoidance evolve jointly, and how such evolution is predicted to feedback to affect evolution of polyandry, still remains largely unknown. While pre-copulatory inbreeding avoidance can facilitate evolution of polyandry under some restrictive conditions [@Duthie], the opportunity for post-copulatory choice might facilitate evolution of polyandry under a much wider range of conditions by allowing females to bias fertilisation toward non-kin. <!--- Just fix this last sentence somehow... --->
